API design for machine learning software: experiences from the scikit-learn project

### 2013-08-09 paper.tex
Revert 7fed4161ba317fedc63b79ee3f34ce946246f5fa (geh?!)

To illustrate the initialize-fit sequence,
let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as the following
example.
\begin{pythoncode}
from clean.linear_model import LogisticRegression

@@

In \sklearn, classical learning algorithms are not the only objects to be
implemented as estimators. For examplee, preprocessing routines (e.g., scaling of
features) or feature extraction techniques (e.g., vectorization of text
documents) also implement the \textit{estimator} interface. Even stateless
processing steps, that do not require the \texttt{fit} method to
perform useful work, implement the estimator interface. As we will illustrate
in the next sections, this design pattern is indeed of prime importance for
consistency, composition and model selection reasons.

>>>>

To illustrate the initialize-fit sequence,
let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as the following
example.
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression

@@

In \sklearn, classical learning algorithms are not the only objects to be
implemented as estimators. For example, preprocessing routines (e.g., scaling of
features) or feature extraction techniques (e.g., vectorization of text
documents) also implement the \textit{estimator} interface. Even stateless
processing steps, that do not require the \texttt{fit} method to
perform useful work, implement the estimator interface. As we will illustrate
in the next sections, this design pattern is indeed of prime importance for
consistency, composition and model selection reasons.
